---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# shelbyR

<!-- badges: start -->
<!-- badges: end -->

## Installation

You can install the development version of shelbyR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("shelby-housing/shelbyR")
```

## Read bids

This is a basic example which shows you how to solve a common problem:

```{r example}
library(shelbyR)
## basic example code
```

# Functions

Data:

- **`shelbyR_raw_paths`**: A tibble with file shorthand, basepath to the file, file pattern to search for, and excel sheet.

```{r, eval=FALSE}
shelbyR::shelbyR_raw_paths
```

File functions:

- **`shelbyR_set_path`**: Set the path to your Lead + Rehab folder.
- **`shelbyR_get_path`**: Get the file path to rehab file(s).
- **`shelbyR_cache_dir`**: Get file path to the shelbyR cache folder. 

Get functions:

- **`shelbyR_read_dataraw`**: Read the specified excel file.
- **`shelbyR_update_cache`**: WORK IN PROGRESS
- **`read_bids`**: Read bids for a specified bid date ("YYYY-MM-DD" format).
- **`get_register`**: Scrape the register's website.

- **`get_rehab_data`**: TODO: rename actually a tidy function
- **`get_bid_dates`**: TODO: actually a tidy function for pulling bid dates from log files.

Tidy functions:

- **`clean_string`**: Combines multiple stringr functions to clean strings. With no params set, only runs `stringr::str_squish()`.
  - **case**: "title", "title up", "lower", "upper", or FALSE (the default)
  - **punct**: Set to FALSE to replace punctuation & symbols with a space (default TRUE)
  - **spaces**: Set to FALSE to remove all spaces (default TRUE)
- **`clean_columns`**: Combines `janitor::clean_names()` and `remove_empty("cols")`
  - **sort**: Organize columns by name (default FALSE)
  - **all_character**: Change all columns to character format.
- **`clean_address`**: Clean/Separate an address column.

- **`cleaner_adr`**: PENDING REMOVAL. 
- **`clean_rehab`**: PENDING REMOVAL.
- **`clean_idis`**: PENDING REMOVAL.
